How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures, to mesoscopic patterns, and down to the  granular constituents that comprise a porous medium.

>>>>

The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the  granular constituents that comprise a porous medium \cite{zareei2022temporal}.
